---
title: "The New `dataverse` Client Package"
author: "__Shiro Kuriwaki__"
institute: "Harvard University<br>(To be Assistant Professor, Yale University)"
date: "February 2021<br>Toronto Data Workshop"
output:
  xaringan::moon_reader:
    css: ["default", "xaringan_style.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '5:4'
      beforeInit: "https://platform.twitter.com/widgets.js"
---

class: middle


```{r include = FALSE}
library(tidyverse)
library(knitr)
library(dataverse)

# data types
library(haven)

# to strip off later
library(readxl)
```


```{r include = FALSE}
weo <- read_excel("data/input/WEO-2018.xlsx")
data(gss_cat)
```


```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)
```


# Table of Contents

* [<b>Dataverse Workflow</b>](#ch_workflow)
* [<b>dataverse clients: Brief History</b>](#ch_history)
* [<b>get_*() functions</b>](#ch_get)
* [<b>pyDataverse</b>](#ch_python)


---
layout: true
<div class="my-footer"><span>Workflow</span></div>
---
class: middle
name: ch_workflow

# Dataverse workflow

## Replication _of_ datasets
## Dataverse
## Workflow in the GUI

---
layout: true
<div class="my-footer"><span>Dataverse History</span></div>
---
class: middle
name: ch_history

# Brief History of Dataverse Clients

## dvn
## dataverse (2017)
## dataverse (2020)

---
layout: true
<div class="my-footer"><span>Dataset retrieval</span></div>
---
class: middle
name: ch_get

# Dataset Retrieval

## get_dataframe_by_*
## Non-tabular datasets
## Options: versions, variables

---
layout: true
<div class="my-footer"><span>pyDataverse</span></div>
---
class: middle
name: ch_python

# Python vs. R clients


---

